Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-04-10 main.tex
clear/add comments

@@

\apt{How is this definition of contoured traces connected to the various properties
  below (which seem to talk about an (uncontoured) trace plus a single contour) ?}
\leo{It only appears in the $C_i$ part of the stack safety property}

@@

@@

>>>>

\apt{This definition may need refinement to reflect the fact that entry and exit sequences
  are multiple instructions; in the middle of these sequences the state might be neither $\ME$ nor $\NOTME$.}

@@

@@

\apt{This definition seems to have vestiges of being based on contoured
  traces; for single contours, there is no possibility of changing from
  $\bot$ to anything else.}

@@

\apt{Does this differ from lockstep equivalence?}
